Multimodal Corpora

### 2017-01-16 paper.tex
Fix spelling error
Fix more spelling errors
Add rest for the second corpus

	\section{The CALLAS Expressivity Corpus}
		The yet to be released CALLAS Expressivity Corpus is part of the \gls{callas} project \cite{2010MultimodalCorpusForGestureExpressivity}. It was introduced in 2010 \cite{2010MultimodalCorpusForGestureExpressivity} and further described in \cite{Caridakis2013} three years later. All the information in this section is taken from those two papers if not stated otherwise, as this corpus was not released to the public yet, so there is no other information source besides a paper from one of the collaborators\cite{wagner:2011:1}. This corpus was a collaborative work between the National Technical University of Athens (G. Caridakis, A. Raouzaiou, K. Karpouzis), the Augsburg University (J. Wagner, F. Lingenfelser, E. Andre) and Humanware S.r.l. (Z. Curto). The available modalities are audio, video and hand gestures recorded separately in three different ways. 
		\subsection{Motivation}
			The main focus for this corpus was to capture cross-cultural differences in expressing emotions with hand gestures. Obtaining the data which is needed to investigate the differences in cultures was done by collecting data in Greece, Germany and Italy as well. Another motivation was the recording of material which is as realistic as possible. This led the team to use persons without any background as actor, with the result that the data's variance is high, which is better to model the real world as the emotion expression of humans may vary greatly.
		\subsection{Recording Scenario}
			The conducted experiment is split into three blocks which are then again split in three smaller parts. The difference between those bigger blocks is the emotion, which should be expressed by the proband. The method used to set the proband in a specific emotional mood was the Velten Mood Induction method \cite{VeltenJr1968473}. Using this method the user was free to modify the given sentence and was encouraged to make a gesture fitting the emotional mood. In the smaller sections three different gesture capturing methods were used.
		\subsubsection{Experiment Setup}
			Many devices were used to record the data which are then incorporated into the corpus. The sentence to read aloud is projected onto the wall in front of the proband. Behind the user is a neutral background. Two cameras are positioned before the proband to capture the face and one to capture the whole upper body. They have a resolution of 720x576px, 24bit color depth and 25 fps. Audio was recorded using a microphone above the head with a samplerate of 16 kHz as mono. Gestures were recorded using a computer vision approaches to detect the hands and the head, a Nintendo Wii remote for each hand or a data glove from Humanware. All datastreams were synchronized with a global clock by \gls{ssi} \cite{SmartSensorIntegration2010}.
		\subsection{Recorded Data}
			The corpus has 15 hours 14 minutes and 24 seconds of footage from all the three modalities. Audio is given by the sound which is recorded by the microphone. Video is available in two channels as two cameras were used for recording. One channel has shows the face and shoulder from the user. The other camera recorded the whole upper body including the hands, which is then used for gesture recognition. Gestures were captured by using three different methods. The first method was to use the video of the second camera which is then used to calculate the 2d position of the hand. The second method was to use the Wii remote to track the hands by capturing the data from the inbuilt accelerometer. The last approach to analyze the gestures executed by the probands is to use the data glove from Humanware which records the angles between the finger joints.
		\subsection{Application}
			c
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

	\section{The CALLAS Expressivity Corpus}
		The yet to be released CALLAS Expressivity Corpus is part of the \gls{callas} project \cite{2010MultimodalCorpusForGestureExpressivity}. It was introduced in 2010 \cite{2010MultimodalCorpusForGestureExpressivity} and further described in \cite{Caridakis2013} three years later. All the information in this section is taken from those two papers if not stated otherwise, as this corpus was not released to the public yet, so there is no other information source besides a paper from one of the collaborators\cite{wagner:2011:1}. This corpus was a collaborative work between the National Technical University of Athens (G. Caridakis, A. Raouzaiou, K. Karpouzis), the Augsburg University (J. Wagner, F. Lingenfelser, E. Andre) and Humanware S.r.l. (Z. Curto). The available modalities are audio, video and hand gestures recorded separately in three different ways. 
		\subsection{Motivation}
			The main focus for this corpus was to capture cross-cultural differences in expressing emotions with hand gestures. Obtaining the data which is needed to investigate the differences in cultures was done by collecting data in Greece, Germany and Italy as well. Another motivation was the recording of material which is as realistic as possible. This led the team to use persons without any background as actor, with the result that the data's variance is high, which is better to model the real world as the emotion expression of humans may vary greatly.
		\subsection{Recording Scenario}
			The conducted experiment is split into three blocks which are then again split in three smaller parts. The difference between those bigger blocks is the emotion, which should be expressed by the proband. The method used to set the proband in a specific emotional mood was the Velten Mood Induction method \cite{VeltenJr1968473}. Using this method the user was free to modify the given sentence and was encouraged to make a gesture fitting the emotional mood. In the smaller sections three different gesture capturing methods were used.\\
			Many devices were used to record the data which are then incorporated into the corpus. The sentence to read aloud is projected onto the wall in front of the proband. Behind the user is a neutral background. Two cameras are positioned before the proband to capture the face and one to capture the whole upper body. They have a resolution of 720x576px, 24bit color depth and 25 fps. Audio was recorded using a microphone above the head with a samplerate of 16 kHz as mono. Gestures were recorded using a computer vision approaches to detect the hands and the head, a Nintendo Wii remote (often called Wiimote) for each hand or a data glove from Humanware. All datastreams were synchronized with a global clock by \gls{ssi} \cite{SmartSensorIntegration2010}.
		\subsection{Recorded Data}
			The corpus has 15 hours 14 minutes and 24 seconds of footage from all the three modalities. Audio is given by the sound which is recorded by the microphone. Video is available in two channels as two cameras were used for recording. One channel has shows the face and shoulder from the user. The other camera recorded the whole upper body including the hands, which is then used for gesture recognition. Gestures were captured by using three different methods. The first method was to use the video of the second camera which is then used to calculate the 2d position of the hand. The second method was to use the Wii remote to track the hands by capturing the data from the inbuilt accelerometer. The last approach to analyze the gestures executed by the probands is to use the data glove from Humanware which records the angles between the finger joints.
		\subsection{Application}
			The primary motivation for the creation of the Callas Expressivity Corpus was to study the cross cultural differences in gesturing under specific emotions. In both publications \cite{2010MultimodalCorpusForGestureExpressivity, Caridakis2013} the approach for this study was only briefly mentioned and was said to be future work. The only thing presented in this context was the feature extraction on the gesture channel of the corpus. Some of these features were overall activation, which represents how much the hands have moved executing a single gesture, the gesturing space, which estimates the space needed for the gesture, and fluidity, which separates abrubt from smooth and elegant gestures. The difficulty of this feature extraction was to find features, which could be calculated from all three capturing methods(bare hands, Wiimote and data glove) or at least finding features which describe similar things. For the computer vision method the movements of the hand inside of the video was used to derive the presented features. The data from the Wiimote could be used similarly to the data derived from the video as the position could be calculated from the accelerometer data recorded from it. The only difference is that with the Wii remote one can calculate the three dimensional position, which is not trivial for the first method. The third method used a data glove where the angles of the finger joints can be recorded. This was used to calculate similar features as the first two methods by using the movements of the fingers instead of the whole hand. \\
			Another use case for this corpus is to test the impact of modalities on emotion recognition, which is shortly described in \cite{Caridakis2013}. They used the audio and video streams from the corpus and examined the goodness of the classifier for four different combinations of features using the Leave-One-Speaker-Out approach. The fist classifier was only trained on audio, the second only on video, the third on both and the fourth classification was done with an decision fusion method. Decision fusion methods train a classifier for each modality and make the decision for a class using the predictions of the underlying classificators. This was tested on the German sub-copus as well as for the Italian sub-corpus. The results have shown that using all modalities or using a decision fusion approach increases the goodness of the classification compared to the cases where classificators were trained with a single modality. Another finding was that classificator which were trained on the Italian sub-corpus had a worse result when applied to the german sub-corpus than using the classifier trained on the German one. The same holds true for a classifier trained on the German parts and applied to the Italian one. Training on both languages delivered a worse result than the specifically trained classifier, but the difference was not too big, which then came with the advantage that the generalization was better. Another work from the German part of the team can be found in \cite{wagner:2011:1}, which describes a similar use case. There they have used the video, audio as well as the gestural modality and compared different feature fusion and decision fusion methods against another. 
